---
title: "nÜkraine slides"
format: revealjs
editor: source
---

``` {r, warning=FALSE}

library(tidyverse)
library(dplyr)
library(haven)
library(RColorBrewer)

```

``` {r, warning=FALSE}

dif <- as.data.frame(read.csv("OXF.csv", sep = ";"))
survey <- data.frame(job=as.factor(dif$V29), volunteer=as.factor(dif$V34))
survey2 <- survey %>% 
  group_by(volunteer, job) %>% 
  summarise(count = n()) %>% 
  mutate(perc = count/sum(count))

```

# Volunteering in the times of war: what data can tell us

# How many people in Ukraine become volunteers since 24.02

``` {r, warning=FALSE}

ggplot(survey2, aes(volunteer)) + 
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "#FDDB52") + 
  scale_y_continuous(labels=scales::percent) +
  ylab("% of all respondents")

```
 TEXT around 70% became volunteers


# How many volunteers lost their jobs

``` {r, warning=FALSE}

ggplot(survey2, aes(x=volunteer, y = perc*100)) +
  geom_bar(aes(fill=job), stat="identity", width = 0.7) +
  labs(x = "Volunteering", y = "% of volunteers", fill = "Financial situation") +
  scale_fill_brewer(palette="Pastel1")

```

Among volunteers, x% lost their jobs

# How many volunteers came back to work beacuse they were out of money

No info

# How many NGO were created

Prior to the Russian invasion of Ukraine there [were](https://www.humanitarianoutcomes.org/sites/default/files/publications/ukraine_review_2022.pdf) about **150 active national NGOs** involved in humanitarian aid. 

Three months after February 24, approximately **2400 new groups** [were registered](https://business.diia.gov.ua/cases/novini/ukrainskij-biznes-v-umovah-vijni-analitika-stanu-za-3-misaci) as "charitable foundations or public organisations".

### How much money were donated by people of different countries to Ukraine 

Since February 24, 992 grants worth $1,228,860,746 [were donated](https://topics.candid.org/issue-pages/ukraine/#tab-nav) to Ukraine. 

# Data on Ukraine

# Google search Ukraine

``` {r, warning=FALSE}

gig <- as.data.frame(read.csv("google.csv", sep = ";"))
google <- data.frame(Search_Ukraine=as.numeric(as.character(gig$Search_Ukraine)), Week=as.Date(gig$Week))

ggplot(google, aes(Week, Search_Ukraine)) +
  geom_area(fill="#dea5a4")

```

# Donations to Ukraine in usd




# Humanitarian help in tonnes



# Military support in vehicles



# Investments in Ukraine (USD)


