---
title: "nÜkraine slides"
format: revealjs
editor: source
---

```{r, warning=FALSE, error=FALSE, include=FALSE}

library(tidyverse)
library(dplyr)
library(haven)
library(RColorBrewer)

```

```{r, warning=FALSE, error=FALSE, include=FALSE}

dif <- as.data.frame(read.csv("OXF.csv", sep = ";"))
dif %>% filter(dif$V34new > 0)
dif %>% filter(dif$V34new <= 7)
dif <- na.omit(dif)

survey <- data.frame(job=as.factor(dif$V29), volunteer=as.factor(dif$V34new))

```

---

## Volunteering in the times of war: what data can tell us

------------------------------------------------------------------------

### How many people in Ukraine become volunteers since 24.02

- Since February 24, more than 60% of people in Central and Western regions of Ukraine became volunteers.

- They helped either physically or financially or both.

- Around 15% of people said they **would** help. Only 25% of people said they had not helped and would not do so.

------------------------------------------------------------------------

### How many people in Ukraine become volunteers since 24.02

```{r, warning=FALSE}

ggplot(survey, aes(volunteer)) + 
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "#dea5a4", width = 0.6) + 
  scale_y_continuous(labels=scales::percent) +
  labs(title = "Are you involved in any kind of volunteering activities to help army/TDF/IDP?", y = "% of all respondents", caption = "Survey by Democratic Intiatives Foundation, May 7-15, Central and Western regions of Ukraine, N = 1000") +
  theme(axis.title.x = element_blank()) +
  theme(plot.caption = element_text(hjust = 1, size = 7)) +
  scale_x_discrete(labels = c("Yes", 
                              "No, but I intend to",
                              "No, and I don't intend to"))

```

---
### How many volunteers lost their jobs

- Around a half of those who volunteered did not lose their jobs. 

- Up to 10% of volunteers said they lost their jobs. 

- Another 10% of them did not lose their jobs because they did not have ones.
---

### How many volunteers lost their jobs

```{r, warning=FALSE}

ggplot(survey, aes(volunteer, fill = job)) + 
  geom_bar(aes(y = (..count..)/sum(..count..)), width = 0.6) + 
  scale_y_continuous(labels=scales::percent) +
  labs(title = "Are you involved in any kind of volunteering activities to help army/TDF/IDP?", y = "% of all respondents", caption = "Survey by Democratic Intiatives Foundation, May 7-15, Central and Western regions of Ukraine, N = 1000") +
  theme(axis.title.x = element_blank()) +
  theme(plot.caption = element_text(hjust = 1, size = 7)) +
  guides(fill=guide_legend(title="Have you lost your job\nsince the invasion?")) +
  scale_fill_manual(labels=c("Yes", "Yes, but found a new one", "No, I didn't have a job to lose", "No, but I don't receive a salary", "No", "Hard to say"), values=c("#F65454", "#F68D54", "#F6B954", "#F6EC54", "#5499F6", "#7E8185")) +
  scale_x_discrete(labels = c("Yes", "No, but I intend to", "No, and I don't intend to"))

```

---
### How many volunteers came back to work beacuse they were out of money

- NO INFO found

---

### How many NGO were created

- Prior to the Russian invasion of Ukraine there [were](https://www.humanitarianoutcomes.org/sites/default/files/publications/ukraine_review_2022.pdf) about **150 active national NGOs** involved in humanitarian aid.

- Three months after February 24, approximately **2400 new groups** [were registered](https://business.diia.gov.ua/cases/novini/ukrainskij-biznes-v-umovah-vijni-analitika-stanu-za-3-misaci) as "charitable foundations or public organisations".

---

### How much money were donated by people of different countries to Ukraine

- Since February 24, 992 grants worth \$1,228,860,746 [were donated](https://topics.candid.org/issue-pages/ukraine/#tab-nav) to Ukraine.
